A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-08-30 paper/authors.tex
update ms

%
% MUSCAT3 Collaborators
%
\author[0000-0001-8511-2981]{N. Narita}
\affiliation{Komaba Institute for Science, The University of Tokyo, 3-8-1 Komaba, Meguro, Tokyo 153-8902, Japan}
\affiliation{Japan Science and Technology Agency, PRESTO, 3-8-1 Komaba, Meguro, Tokyo 153-8902, Japan}
\affiliation{Astrobiology Center, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-4909-5763]{A. Fukui} % afukui@g.ecc.u-tokyo.ac.jp
\affiliation{Komaba Institute for Science, The University of Tokyo, 3-8-1 Komaba, Meguro, Tokyo 153-8902, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-5658-5971]{Masahiro Ikoma} % ikoma.masahiro@gmail.com
\affiliation{Division of Science, National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}

\author[0000-0002-6510-0681]{M. Tamura} % motohide.tamura@nao.ac.jp
\affiliation{Department of Astronomy, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
\affiliation{Astrobiology Center, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}
\affiliation{National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}

% AO IMAGING
\author[0000-0002-2532-2853]{S. B. Howell}
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

>>>>

%
% MUSCAT3 Collaborators
%
\author[0000-0001-8511-2981]{N. Narita}
\affiliation{Komaba Institute for Science, The University of Tokyo, Tokyo 153-8902, Japan}
\affiliation{Japan Science and Technology Agency, PRESTO, Tokyo 153-8902, Japan}
\affiliation{Astrobiology Center, Tokyo 181-8588, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-4909-5763]{A. Fukui} % afukui@g.ecc.u-tokyo.ac.jp
\affiliation{Komaba Institute for Science, The University of Tokyo, Tokyo 153-8902, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-5658-5971]{Masahiro Ikoma} % ikoma.masahiro@gmail.com
\affiliation{Division of Science, National Astronomical Observatory of Japan, Tokyo 181-8588, Japan}

\author[0000-0002-6510-0681]{M. Tamura} % motohide.tamura@nao.ac.jp
\affiliation{Department of Astronomy, University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Astrobiology Center, Tokyo 181-8588, Japan}
\affiliation{National Astronomical Observatory of Japan, Tokyo 181-8588, Japan}

% AO IMAGING
\author[0000-0001-9800-6248]{E. Furlan} % furlan@ipac.caltech.edu
\affiliation{NASA Exoplanet Science Institute, Caltech/IPAC, Pasadena, CA 91125, USA}

\author[0000-0003-2519-6161]{C.~L.~Gnilka} % clgnilka@gmail.com
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

\author[0000-0002-9903-9911]{K.~V.~Lester} % klester192@gmail.com
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

\author[0000-0002-2532-2853]{S. B. Howell}
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
